### 2021-11-02 paper/pldi22/formal.tex
More formalization

\[
  \begin{array}{lr@{~}c@{~}c@{~}c@{~}l}
    \text{Programs} & \progset &\ni& \prog &=& (\istset, \getfunc, \getinst,
    \getnext)\\

@@

An $\ires$ program $\prog = (\istset, \getfunc, \getinst, \getnext) \in \progset $
consists of initial states and three mappings; $\getfunc: \labset \rightarrow
\funcset$ and $\getinst: \labset \rightarrow \instset$ map labels to their
functions and instructions, respectively, and $\getnext: \labset \rightarrow
\labset$ maps labels to their next labels, where a label $\lab \in \labset$
denotes a program point.  A function $\func \in \funcset$ is defined with its
parameters and body label.  For presentation brevity, we assume that no global
or captured variables exist in this paper.  An instruction $\inst \in \instset$
is an assignment $\refer \kweq \expr$, an object allocation $\varx \kweq \kwcl \kwcr$, a
function call $\varx \kweq \expr \kwrl \expr^* \kwrr$, a branch $\kwif \; \expr \;
\lab \; \lab$, or a return instruction $\kwret \; \expr$.  An invocation of an
abstract algorithm in ECMAScript is compiled to a function call instruction with
a new temporary variable.  We represent loops using branch instructions with
cyclic pointing of labels in $\getnext$.  An expression is a primitive value
$\pval$, an operation $\op \kwrl \expr^* \kwrr$, or a reference $\refer$.  A
reference is a variable $\varx$ or an object field $\expr \kwsl \expr \kwsr$.
We write $\expr.\varf$ to briefly represent $\expr \kwsl \code{"f"} \kwsr$.

@@

The concrete semantics $\sem{\prog}$ of an $\ires$ program $\prog = (\istset,
\getinst, \getnext)$ is defined as follows:
\[
  \sem{\prog} = \{ \st \in \stset \mid \ist \in \istset \wedge \ist \trans^* \st \}
\]
where $\trans^*$ denotes one or more repetition of $\trans$, and $\st \trans
\st'$ if and only if $\st = (\lab, \_, \_, \_)$ and $\sem{\getinst(\lab)}(\st) =
\st'$. Another way to represent the concrete semantics is to define a transfer
function $\transfer: \powerset{\stset} \rightarrow \powerset{\stset}$:
\[
  \sem{\prog} = \lim_{n \rightarrow \infty}\transfer^n(\istset)
\]
where $\transfer(S) = \{ \st' \mid \st \in S \wedge \st \trans \st' \}$.  Now,
we define the denotational semantics of expressions, instructions, and
functions.

@@

            \tree_j
            & \text{if} \; \val_0 = \ty_k \langle \tree_1, \cdots, \tree_n
            \rangle \wedge \val_1 = j\\
          \end{array}
        \right.\\
      \end{array}
    \]
\end{itemize}

@@

\begin{itemize}
  \item \underline{Variable Assignments}:
    \[
      \sem{\varx \kweq \expr}(\st) =
      (\getnext(\lab), \ctxts, \heap, \env[\varx \mapsto \val])
    \]
    where $\sem{\expr}(\st) = ((\lab, \ctxts, \heap, \env), \val)$

  \item \underline{Field Assignments}:
    \[
      \sem{\expr_0 \kwsl \expr_1 \kwsr \kweq \expr_2}(\st) =
      (\getnext(\lab), \ctxts, \heap[\addr \mapsto \obj'], \env)
    \]
    where
    \[
      \begin{array}{l@{~}c@{~}ll}
        \sem{\expr_0}(\st) &=& (\st', \addr) &\wedge\\
        \sem{\expr_1}(\st') &=& (\st'', \str) &\wedge\\
        \sem{\expr_2}(\st'') &=& ((\lab, \ctxts, \heap, \env), \val) &\wedge\\
        \obj &=& \heap(\addr) &\wedge\\
        \obj' &=& \obj[\str \mapsto \val]\\
      \end{array}
    \]

  \item \underline{Object Allocations}:
    \[
      \sem{\varx \kweq \kwcl \kwcr}(\st) =
      (\lab, \ctxts, \heap[\addr \mapsto \varnothing], \env[\varx \mapsto
      \addr])
    \]
    where $\st = (\lab, \ctxts, \heap, \env) \wedge \addr \not\in
    \text{Domain}(\heap)$

  \item \underline{Function Calls}:
    \[
      \sem{\varx \kweq \expr \kwrl \expr_1 \cdots \expr_n \kwrr}(\st) =
      (\lab_\varf, \ctxt :: \ctxts, \heap, \env')
    \]
    where
    \[
      \begin{array}{l@{~}c@{~}ll}
        \sem{\expr}(\st) &=& (\st_0, \kwdef \; \kwrl \varx_1, \cdots, \varx_n
        \kwrr \; \lab_\varf) &\wedge\\
        \sem{\expr_j}(\st_{j-1}) &=& (\st_j, \val_j) \;
        [\forall 1 \leq j \leq n] &\wedge\\
        \st_n &=& (\lab, \ctxts, \heap, \env) &\wedge\\
        \env' &=& [\varx_1 \mapsto \val_1, \cdots, \varx_n \mapsto \val_n]
        &\wedge\\
        \ctxt &=& (\getnext(\lab), \env, \varx)\\
      \end{array}
    \]

@@

We define a \textit{partial evaluation} $\peval{-}: \progset \rightarrow
\atreeset \rightarrow \progset$ of $\ires$ programs to specialize JavaScript
semantics with a given syntactic view:
\[
  \peval{\prog}(\atree) = \transform{\prog} \circ \asem{\prog} (\atree)
\]
It takes a syntactic view $\atree \in \atreeset$ to restrict arguments of the
corresponding \esalg{Evaluation} function. Then, it performs a static analysis
$\asem{-}$ of a given program $\prog$ with the syntactic view $\atree$ and
transforms the program using $\transform{-}$ with the analysis result
$\asem{\prog}(\atree)$ to produce a specialized $\ires$ program.  Since the
\esalg{Evaluation} of $\ty$ might one or more $\ires$ functions, we only define
the partial evaluation when $\atree = \ty_k \langle \cdots \rangle$.  Now, we
define the static analysis and program transformation of $\ires$ programs and
prove the semantics preservation of the partial evaluation consisting of them.

@@

The static analysis $\asem{\prog}(\atree)$ performs an abstract
interpretation~\cite{ai1977, ai1992} to abstract concrete semantics under the
given given syntactic view $\atree$.  We first define abstract domains of
states, calling contexts, environments, and values as follows:
\begin{itemize}
  \item \underline{Abstract States}:
    $\aelemset = \amctxtset \times \atctxtset \times \afsenvset$
    \[
      \begin{array}{lcl}
        \aelemgamma(\amctxt, \atctxt, \afsenv) &=&
        \amctxtgamma(\amctxt) \cup
        (\atctxtgamma(\atctxt) \cap \afsenvgamma(\afsenv))\\

        (\amctxt, \atctxt, \afsenv) \order
        (\amctxt', \atctxt', \afsenv') &\Leftrightarrow&
        (\amctxt \order \amctxt') \wedge
        (\atctxt \order \atctxt') \wedge
        (\afsenv \order \afsenv')\\

        (\amctxt, \atctxt, \afsenv) \join (\amctxt', \atctxt', \afsenv') &=&
        (\amctxt \join \amctxt', \atctxt \join \atctxt', \afsenv \join \afsenv')\\
      \end{array}
    \]

  \item \underline{Merged Calling Contexts}:
    $\amctxtset = \powerset{\labset}$
    \[
      \begin{array}{lcl}
        \amctxtgamma(\amctxt) &=& \{ \st \in \stset \mid
          \st = (\lab, [\ctxt_1, \cdots, \ctxt_n], \_, \_) \wedge\\&&

@@

          \phantom{\{ \st \in \stset \mid}
          \lab_j \in \amctxt
        \}\\

        \amctxt \order \amctxt' &\Leftrightarrow&
        \amctxt \subseteq \amctxt\\

        \amctxt \join \amctxt' &=&
        \amctxt \cup \amctxt\\
      \end{array}
    \]

  \item \underline{Target Calling Contexts}:
    $\atctxtset = \powerset{\labset \times \funcset}$
    \[
      \begin{array}{lcl}
        \atctxtgamma(\atctxt) &=& \{ \st \in \stset \mid
          \st = (\lab_0, [\ctxt_1, \cdots, \ctxt_n], \_, \_) \wedge\\&&

@@

          \phantom{\{ \st \in \stset \mid}
          \exists 0 \leq m \leq n. \; \getfunc(\lab_m) = \ty_k.\eval \wedge\\&&

          \phantom{\{ \st \in \stset \mid}
          \forall 1 \leq j \leq m. \; (\lab_j, \getfunc{\lab_{j-1}}) \in \atctxt
        \}\\

        \atctxt \order \atctxt' &\Leftrightarrow& \atctxt \subseteq \atctxt\\

        \atctxt \join \atctxt' &=& \atctxt \cup \atctxt'\\
      \end{array}
    \]

  \item \underline{Flow-Sensitive Abstract Environments}:
    $\afsenvset = \labset \rightarrow \aenvset$
    \[
      \begin{array}{lcl}
        \afsenvgamma(\afsenv) &=& \{ \st \in \stset \mid
          \st = (\lab, \_, \_, \_) \wedge \st \in \aenvgamma(\afsenv(\lab))
        \}\\

@@

  \item \underline{Abstract Environments}:
    $\aenvset = \varset \rightarrow \aenvset$
    \[
      \begin{array}{lcl}
        \aenvgamma(\aenv) &=& \{ \st \in \stset \mid
          \forall \varx \in \varset. \;
          \sem{\varx}(\st) \in \avalgamma(\aenv(\varx))
        \}\\

@@

  \item \underline{Abstract Values}: $\avalset = \valset \uplus \atreeset \uplus
    \{ \top, \bot,  \}$
    \[
      \begin{array}{lcl}
        \avalgamma(\aval) &=& \left\{
          \begin{array}{ll}
            \{ \val \} & \text{if} \; \aval = \val\\
            \atreegamma(\atree) & \text{if} \; \aval = \atree\\
            \valset & \text{if} \; \aval = \top\\
            \varnothing & \text{if} \; \aval = \bot\\
          \end{array}
        \right.\\

@@

An abstract state $\aelem \in \aelemset$ is a triple of a merged and target call
edges and a flow-sensitive abstract environment.  A merged calling context
$\amctxt \in \amctxtset$ is a set of call labels representing merged function
calls. A target calling context $\atctxt \in \atctxtset$ is a set of possible
static call edges from labels to function, and it represents the scope of static
analysis. To more precisely represent states in target calling contexts, we
define a flow-sensitive abstract environment $\afsenv \in \afsenvset$. It is
a mapping from labels to abstract environments to represents the shape of
environments in each label. An abstract environment $\aenv \in \aenvset$ is a
mapping from variables to abstract values to describe values stored in
variables. An abstract value $\aval \in \avalset$ is a static value $\val$, a
syntactic view $\atree$, a dynamic value $\top$, or nothing $\bot$.  Now, we
define abstract semantics of expressions, instructions, and programs.

@@

            \top & \text{otherwise}\\
          \end{array}
        \right.\\
      \end{array}
    \]
  \item \underline{Variable Lookups}:
    \[
      \asem{\varx}(\aenv) = \aenv(\varx)
    \]
  \item \underline{Field Lookups}:
    \[
      \asem{\expr_0 \kwsl \expr_1 \kwsr}(\aenv) = \aval
    \]
    where
    \[
      \begin{array}{l@{~}c@{~}l@{~}l}
        \asem{\expr_0}(\aenv) &=& \aval_0 &\wedge\\
        \asem{\expr_1}(\aenv) &=& \aval_1 &\wedge\\
        \aval &=& \left\{
          \begin{array}{ll}
            \tree_j & \text{if} \;
            \aval_0 = \ty_k \langle \tree_1, \cdots, \tree_n \rangle \wedge
            \aval_1 = j\\

            \atree_j & \text{if} \;
            \aval_0 = \ty_k \langle \atree_1, \cdots, \atree_n \rangle \wedge
            \aval_1 = j\\

@@

\paragraph{Instructions} Then, we define the abstract semantics of instructions
as follows:
\[
  \framebox{$\asem{\inst}: \amctxtset \times \atctxtset \times \labset \times
    \aenvset \rightarrow
  \aelemset$}
\]
\begin{itemize}
  \item \underline{Variable Assignments}:
    \[
      \asem{\varx \kweq \expr}(\amctxt, \atctxt, \lab, \aenv) =
      (\amctxt, \atctxt, [\getnext(\lab) \mapsto \aenv[\varx \mapsto \aval]])
    \]
    where $\aval = \asem{\expr}(\aenv)$

  \item \underline{Field Assignments}:
    \[
      \asem{\expr_0 \kwsl \expr_1 \kwsr \kweq \expr_2}(\amctxt, \atctxt, \lab, \aenv) =
      (\amctxt, \atctxt, [\getnext(\lab) \mapsto \aenv])
    \]

  \item \underline{Object Allocations}:
    \[
      \asem{\varx \kweq \kwcl \kwcr}(\amctxt, \atctxt, \lab, \aenv) =
      (\amctxt, \atctxt, [\getnext(\lab) \mapsto \aenv[\varx \mapsto \top]])
    \]

  \item \underline{Function Calls}:
    \[
      \asem{\varx \kweq \expr \kwrl \expr_1 \cdots \expr_n \kwrr}(\amctxt,
      \atctxt, \lab, \aenv) = (\amctxt', \atctxt', \afsenv)
    \]
    where
    \[
      \begin{array}{l@{~}c@{~}ll}
        \aval &=& \asem{\expr}(\aenv) &\wedge\\
        \aval_j &=& \asem{\expr_j}(\aenv) \; [\forall 1 \leq j \leq n] &\wedge\\
        (\amctxt', \atctxt') &=& \left\{
          \begin{array}{ll}
            (\amctxt, \atctxt \cup \{ (\lab, \func) \} &
            \text{if} \; \aval = \func \wedge \exists j. \; \aval_j \neq \top\\

            (\amctxt \cup \{ \lab \}, \atctxt) &
            \text{otherwise}
          \end{array}
        \right.\\
        \afsenv &=& [ \lab_\func \mapsto \aenv_\func \mid
        (\lab, \func) \in \atctxt' \wedge\\&&

@@

  \item \underline{Branches}:
    \[
      \asem{\kwif \; \expr \; \lab_\vart \; \lab_\varf}(\amctxt, \atctxt, \lab, \aenv) =
      (\amctxt, \atctxt, \afsenv')
    \]
    where
    \[
      \begin{array}{lcl}
        \aval &=& \asem{\expr}(\aenv)\\

        \afsenv &=& \left\{
          \begin{array}{ll}
            [\lab_\vart \mapsto \aenv] & \text{if} \; \true \in
            \avalgamma(\aval)\\
            \varnothing & \text{otherwise}\\
          \end{array}
        \right.\\

        \afsenv' &=& \left\{
          \begin{array}{ll}
            \afsenv[\lab_\varf \mapsto \aenv] & \text{if} \; \false \in
            \avalgamma(\aval)\\
            \afsenv & \text{otherwise}\\
          \end{array}
        \right.\\
      \end{array}
    \]

  \item \underline{Returns}:
    \[
      \asem{\kwret \; \expr}(\amctxt, \atctxt, \lab_0, \aenv) =
      (\amctxt, \atctxt, \afsenv)
    \]
    where
    \[
      \begin{array}{lcl}
        \aval &=& \asem{\expr'}(\aenv)\\

        \func &=& \getfunc(\lab_0)\\
        R &=& \{ (\getnext(\lab), \varx) \mid
          (\lab, \func) \in \atctxt \wedge\\

          && \phantom{\{ (\getnext(\lab), \varx) \mid}
          \getinst(\lab) = \varx \kweq \expr^\lab (\expr^\lab_1 \cdots \expr^\lab_n)
        \}\\

        \afsenv &=& \lambda \lab \in \labset. \; \left\{
          \begin{array}{ll}
            [\varx \mapsto \aval]
            & \text{if} \; (\lab, \varx) \in R\\

            \varnothing
            & \text{otherwise}\\
          \end{array}
        \right.\\
      \end{array}
    \]
\end{itemize}

>>>>

\[
  \begin{array}{lr@{~}c@{~}c@{~}c@{~}l}
    \text{Programs} & \progset &\ni& \prog &=& (\initstset{\prog},
    \getfunc{\prog}, \getinst{\prog}, \getnext{\prog})\\

@@

An $\ires$ program $\prog = (\initstset{\prog}, \getfunc{\prog},
\getinst{\prog}, \getnext{\prog}) \in \progset $ consists of initial states and
three mappings; $\getfunc{\prog}: \labset \rightarrow \funcset$ and
$\getinst{\prog}: \labset \rightarrow \instset$ map labels to their functions
and instructions, respectively, and $\getnext{\prog}: \labset \rightarrow
\labset$ maps labels to their next labels, where a label $\lab \in \labset$
denotes a program point.  A function $\func \in \funcset$ is defined with its
parameters and body label.  For presentation brevity, we assume that no global
or captured variables exist in this paper.  An instruction $\inst \in \instset$
is an assignment $\refer \kweq \expr$, an object allocation $\varx \kweq \kwcl
\kwcr$, a function call $\varx \kweq \expr \kwrl \expr^* \kwrr$, a branch $\kwif
\; \expr \; \lab \; \lab$, or a return instruction $\kwret \; \expr$.  An
invocation of an abstract algorithm in ECMAScript is compiled to a function call
instruction with a new temporary variable.  We represent loops using branch
instructions with cyclic pointing of labels in $\getnext{\prog}$.  An expression
is a primitive value $\pval$, an operation $\op \kwrl \expr^* \kwrr$, or a
reference $\refer$.  A reference is a variable $\varx$ or an object field $\expr
\kwsl \expr \kwsr$.  We write $\expr.\varf$ to briefly represent $\expr \kwsl
\code{"f"} \kwsr$.

@@

The concrete semantics $\sem{\prog}$ of an $\ires$ program $\prog$ is defined as
follows:
\[
  \sem{\prog} = \{ \st \in \stset \mid \initst \in \initstset{\prog} \wedge
  \initst \trans{\prog}^* \st \}
\]
where $\trans{\prog}^*$ denotes one or more repetition of $\trans{\prog}$, and
$\st \trans{\prog} \st'$ if and only if $\st = (\lab, \_, \_, \_)$ and
$\sem{\getinst{\prog}(\lab)}(\st) = \st'$. Another way to represent the concrete
semantics is to define a transfer function $\transfer: \powerset{\stset}
\rightarrow \powerset{\stset}$:
\[
  \sem{\prog} = \lim_{n \rightarrow \infty}\transfer^n(\initstset{\prog})
\]
where
\begin{equation}\label{eqn:transfer}
  \transfer(S) = \{ \st' \mid \st \in S \wedge \st \trans{\prog} \st' \}
\end{equation}
Now, we define the denotational semantics of expressions, instructions, and
functions.

@@

            \tree_j
            & \text{if} \; \val_0 = \ty_k \langle \tree_1, \cdots, \tree_n
            \rangle \wedge \val_1 = j\\

            \ty_k.\eval
            & \text{if} \; \val_0 = \ty_k \langle \tree_1, \cdots, \tree_n
            \rangle \wedge \val_1 = \code{"eval"}\\
          \end{array}
        \right.\\
      \end{array}
    \]
\end{itemize}

@@

\begin{itemize}
  \item \underline{Variable Assignments}:
    \[
      \sem{\varx \kweq \expr}(\st) =
      (\getnext{\prog}(\lab), \ctxts, \heap, \env[\varx \mapsto \val])
    \]
    where $\sem{\expr}(\st) = ((\lab, \ctxts, \heap, \env), \val)$

  \item \underline{Field Assignments}:
    \[
      \sem{\expr_0 \kwsl \expr_1 \kwsr \kweq \expr_2}(\st) =
      (\getnext{\prog}(\lab), \ctxts, \heap[\addr \mapsto \obj'], \env)
    \]
    where
    \[
      \begin{array}{l@{~}c@{~}ll}
        \sem{\expr_0}(\st) &=& (\st', \addr) &\wedge\\
        \sem{\expr_1}(\st') &=& (\st'', \str) &\wedge\\
        \sem{\expr_2}(\st'') &=& ((\lab, \ctxts, \heap, \env), \val) &\wedge\\
        \obj &=& \heap(\addr) &\wedge\\
        \obj' &=& \obj[\str \mapsto \val]\\
      \end{array}
    \]

  \item \underline{Object Allocations}:
    \[
      \sem{\varx \kweq \kwcl \kwcr}(\st) =
      (\lab, \ctxts, \heap[\addr \mapsto \epsilon], \env[\varx \mapsto
      \addr])
    \]
    where $\st = (\lab, \ctxts, \heap, \env) \wedge \addr \not\in
    \text{Domain}(\heap)$

  \item \underline{Function Calls}:
    \[
      \sem{\varx \kweq \expr \kwrl \expr_1 \cdots \expr_n \kwrr}(\st) =
      (\lab_\varf, \ctxt :: \ctxts, \heap, \env')
    \]
    where
    \[
      \begin{array}{l@{~}c@{~}ll}
        \sem{\expr}(\st) &=& (\st_0, \kwdef \; \kwrl \varx_1, \cdots, \varx_n
        \kwrr \; \lab_\varf) &\wedge\\
        \sem{\expr_j}(\st_{j-1}) &=& (\st_j, \val_j) \;
        [\forall 1 \leq j \leq n] &\wedge\\
        \st_n &=& (\lab, \ctxts, \heap, \env) &\wedge\\
        \env' &=& [\varx_1 \mapsto \val_1, \cdots, \varx_n \mapsto \val_n]
        &\wedge\\
        \ctxt &=& (\getnext{\prog}(\lab), \env, \varx)\\
      \end{array}
    \]

@@

We define a \textit{partial evaluation} $\peval{\prog}: \atreeset \rightarrow
\progset$ of $\ires$ programs to specialize JavaScript semantics with a given
syntactic view:
\[
  \peval{\prog}(\atree) = \transform{\prog} \circ \asem{\prog} (\atree)
\]
It takes a syntactic view $\atree \in \atreeset$ to restrict arguments of the
corresponding \esalg{Evaluation} function. Then, it performs a static analysis
$\asem{\prog}$ of a given program $\prog$ with the syntactic view $\atree$, and
transforms the program to a specialized program using $\transform{\prog}$ with
the analysis result $\asem{\prog}(\atree)$.  Since the \esalg{Evaluation} of
$\ty$ might one or more $\ires$ functions, we only define the partial evaluation
when $\atree = \ty_k \langle \cdots \rangle$.  Now, we define the static
analysis and program transformation of $\ires$ programs and prove the semantics
preservation of the partial evaluation consisting of them.

@@

The static analysis $\asem{\prog}(\atree)$ performs an abstract
interpretation~\cite{ai1977, ai1992} to abstract concrete semantics under the
given given syntactic view $\atree$.  We first define abstract domains of
states, call edges, environments, and values as follows:
\begin{itemize}
  \item \underline{Abstract States}: $\aelemset$
    \[
      \begin{array}{lcl}
        \aelemset &=& \adcallset \times \ascallset \times \afsenvset\\

        \aelemgamma &:& \atreeset \rightarrow \aelemset \rightarrow
        \powerset{\stset}\\

        \aelemgamma(\atree)(\aelem) &=&
        (\adcallgamma(\atree)(\adcall) \setminus C) \uplus
        (C \cap \afsenvgamma(\afsenv))\\
        \multicolumn{3}{r}{\text{where} \; C = \ascallgamma(\atree)(\ascall)}\\

        \aelem \order \aelem' &\Leftrightarrow&
        \adcall \order \adcall' \wedge
        \ascall \order \ascall' \wedge
        \afsenv \order \afsenv'\\

        \aelem \join \aelem' &=&
        (\adcall \join \adcall', \ascall \join \ascall', \afsenv \join \afsenv')\\
      \end{array}
    \]
    where $\atree = \ty_k \langle \cdots \rangle$, $\aelem = (\adcall, \ascall,
    \afsenv)$ and $\aelem' = (\adcall', \ascall', \afsenv')$

  \item \underline{Dynamic Call Sets}: $\adcallset$
    \[
      \begin{array}{lcl}
        \adcallset &=& \powerset{\labset}\\

        \adcallgamma &:& \atreeset \rightarrow \adcallset \rightarrow
        \powerset{\stset}\\

        \adcallgamma(\atree)(\adcall) &=& \{ \st \in \stset \mid
          \st = (\lab, [\ctxt_1, \cdots, \ctxt_n], \_, \_) \wedge\\&&

@@

          \phantom{\{ \st \in \stset \mid}
          \lab_j \in \adcall
        \}\\

        \adcall \order \adcall' &\Leftrightarrow&
        \adcall \subseteq \adcall\\

        \adcall \join \adcall' &=&
        \adcall \cup \adcall\\
      \end{array}
    \]
    where $\atree = \ty_k \langle \cdots \rangle$

  \item \underline{Static Call Sets}: $\ascallset$
    \[
      \begin{array}{lcl}
        \ascallset &=& \powerset{\labset \times \funcset}\\

        \ascallgamma &:& \atreeset \rightarrow \ascallset \rightarrow
        \powerset{\stset}\\

        \ascallgamma(\atree)(\ascall) &=& \{ \st \in \stset \mid
          \st = (\lab_0, [\ctxt_1, \cdots, \ctxt_n], \_, \_) \wedge\\&&

@@

          \phantom{\{ \st \in \stset \mid}
          \exists 0 \leq m \leq n. \; \getfunc{\prog}(\lab_m) = \ty_k.\eval
          \wedge\\&&

          \phantom{\{ \st \in \stset \mid}
          \forall 1 \leq j \leq m. \; (\lab_j, \getfunc{\prog}{\lab_{j-1}}) \in
          \ascall
        \}\\

        \ascall \order \ascall' &\Leftrightarrow& \ascall \subseteq \ascall\\

        \ascall \join \ascall' &=& \ascall \cup \ascall'\\
      \end{array}
    \]
    where $\atree = \ty_k \langle \cdots \rangle$

  \item \underline{Flow-Sensitive Abstract Environments}: $\afsenvset$
    \[
      \begin{array}{lcl}
        \afsenvset &=& \labset \rightarrow \aenvset\\

        \afsenvgamma &:& \afsenvset \rightarrow \powerset{\stset}\\

        \afsenvgamma(\afsenv) &=& \{ \st \in \stset \mid
          \st = (\lab, \_, \_, \_) \wedge \st \in \aenvgamma(\afsenv(\lab))
        \}\\

@@

  \item \underline{Abstract Environments}: $\aenvset$
    \[
      \begin{array}{lcl}
        \aenvset &=& \varset \rightarrow \aenvset\\

        \aenvgamma &:& \aenvset \rightarrow \powerset{\stset}\\

        \aenvgamma(\aenv) &=& \{ \st \in \stset \mid
          \forall \varx \in \varset. \;
          \sem{\varx}(\st) \in \avalgamma(\aenv(\varx))
        \}\\

@@

  \item \underline{Abstract Values}: $\avalset$
    \[
      \begin{array}{lcl}
        \avalset &=& \valset \uplus \atreeset \uplus \{ \top, \bot,  \}\\

        \avalgamma &:& \avalset \rightarrow \powerset{\valset}\\

        \avalgamma(\aval) &=& \left\{
          \begin{array}{ll}
            \{ \val \} & \text{if} \; \aval = \val\\
            \atreegamma(\atree) & \text{if} \; \aval = \atree\\
            \valset & \text{if} \; \aval = \top\\
            \varnothing & \text{if} \; \aval = \bot\\
          \end{array}
        \right.\\

@@

An abstract state $\aelem \in \aelemset$ is a triple of a dynamic call set, a
static call set, and a flow-sensitive abstract environment.  A dynamic call set
$\adcall \in \adcallset$ is a set of call labels representing function calls
with multiple functions or no static arguments. A static call set $\ascall \in
\ascallset$ is a set of possible static call edges from labels to function, and
it represent a set of \textit{static calling contexts} $\ascallgamma(\ascall)$
used as the scope of program transformations.  To more precisely in the static
calling contexts, we define a flow-sensitive abstract environment $\afsenv \in
\afsenvset$. It is a mapping from labels to abstract environments to represents
the shape of environments in each label. An abstract environment $\aenv \in
\aenvset$ is a mapping from variables to abstract values to describe values
stored in variables. An abstract value $\aval \in \avalset$ is a static value
$\val$, a syntactic view $\atree$, a dynamic value $\top$, or nothing $\bot$.
Now, we define abstract semantics of expressions, instructions, and programs.

@@

            \top & \text{otherwise}\\
          \end{array}
        \right.\\
      \end{array}
    \]
  \item \underline{Variable Lookups}:
    \[
      \asem{\varx}(\aenv) = \aenv(\varx)
    \]
  \item \underline{Field Lookups}:
    \[
      \asem{\expr_0 \kwsl \expr_1 \kwsr}(\aenv) = \aval
    \]
    where
    \[
      \begin{array}{lcl}
        \asem{\expr_0}(\aenv) &=& \aval_0\\
        \asem{\expr_1}(\aenv) &=& \aval_1\\
        \aval &=& \left\{
          \begin{array}{ll}
            \atree_j & \text{if} \;
            \aval_0 = \ty_k \langle \atree_1, \cdots, \atree_n \rangle \wedge
            \aval_1 = j\\

            \ty_k.\eval & \text{if} \;
            \aval_0 = \ty_k \langle \cdots \rangle \wedge
            \aval_1 = \code{"eval"}\\

@@

\paragraph{Instructions} Then, we define the abstract semantics of instructions
as follows:
\[
  \framebox{$\asem{\inst}: \labset \times \aelemset \rightarrow \aelemset$}
\]
\begin{itemize}
  \item \underline{Variable Assignments}:
    \[
      \asem{\varx \kweq \expr}(\lab, \aelem) =
      (\adcall, \ascall, [\getnext{\prog}(\lab) \mapsto \aenv[\varx
      \mapsto \aval]])
    \]
    where
    \[
      \begin{array}{lcl}
        \aelem &=& (\adcall, \ascall, \afsenv)\\
        \aenv &=& \afsenv(\lab)\\
        \aval &=& \asem{\expr}(\aenv)\\
      \end{array}
    \]

  \item \underline{Field Assignments}:
    \[
      \asem{\expr_0 \kwsl \expr_1 \kwsr \kweq \expr_2}
      (\lab, \aelem) =
      (\adcall, \ascall, [\getnext{\prog}(\lab) \mapsto \aenv])
    \]
    where
    \[
      \begin{array}{lcl}
        \aelem &=& (\adcall, \ascall, \afsenv)\\
        \aenv &=& \afsenv(\lab)\\
      \end{array}
    \]

  \item \underline{Object Allocations}:
    \[
      \asem{\varx \kweq \kwcl \kwcr}(\lab, \aelem) =
      (\adcall, \ascall, [\getnext{\prog}(\lab) \mapsto \aenv[\varx
      \mapsto \top]])
    \]
    where
    \[
      \begin{array}{lcl}
        \aelem &=& (\adcall, \ascall, \afsenv)\\
        \aenv &=& \afsenv(\lab)\\
      \end{array}
    \]

  \item \underline{Function Calls}:
    \[
      \asem{\varx \kweq \expr \kwrl \expr_1 \cdots \expr_n \kwrr}(\lab, \aelem)
      = (\adcall', \ascall', \afsenv')
    \]
    where
    \[
      \begin{array}{l@{~}c@{~}l}
        \aelem &=& (\adcall, \ascall, \afsenv)\\
        \aenv &=& \afsenv(\lab)\\
        \aval &=& \asem{\expr}(\aenv)\\
        \aval_j &=& \asem{\expr_j}(\aenv) \; [\forall 1 \leq j \leq n]\\
        (\adcall', \ascall') &=& \left\{
          \begin{array}{ll}
            (\adcall, \ascall \cup \{ (\lab, \func) \} &
            \text{if} \; \aval = \func \wedge \exists j. \; \aval_j \neq \top\\

            (\adcall \cup \{ \lab \}, \ascall) &
            \text{otherwise}
          \end{array}
        \right.\\
        \afsenv' &=& [ \lab_\func \mapsto \aenv_\func \mid
        (\lab, \func) \in \ascall' \wedge\\&&

@@

  \item \underline{Branches}:
    \[
      \asem{\kwif \; \expr \; \lab_\vart \; \lab_\varf}(\lab, \aelem) =
      (\adcall, \ascall, \afsenv'')
    \]
    where
    \[
      \begin{array}{lcl}
        \aelem &=& (\adcall, \ascall, \afsenv)\\
        \aenv &=& \afsenv(\lab)\\
        \aval &=& \asem{\expr}(\aenv)\\

        \afsenv' &=& \left\{
          \begin{array}{ll}
            [\lab_\vart \mapsto \aenv] & \text{if} \; \true \in
            \avalgamma(\aval)\\
            \epsilon & \text{otherwise}\\
          \end{array}
        \right.\\

        \afsenv'' &=& \left\{
          \begin{array}{ll}
            \afsenv'[\lab_\varf \mapsto \aenv] & \text{if} \; \false \in
            \avalgamma(\aval)\\
            \afsenv' & \text{otherwise}\\
          \end{array}
        \right.\\
      \end{array}
    \]

  \item \underline{Returns}:
    \[
      \asem{\kwret \; \expr}(\lab_0, \aelem) =
      (\adcall, \ascall, \afsenv')
    \]
    where
    \[
      \begin{array}{lcl}
        \aelem &=& (\adcall, \ascall, \afsenv)\\
        \aenv &=& \afsenv(\lab)\\
        \aval &=& \asem{\expr'}(\aenv)\\

        \func &=& \getfunc{\prog}(\lab_0, \aelem)\\
        R &=& \{ (\getnext{\prog}(\lab), \varx) \mid
          (\lab, \func) \in \ascall \wedge\\&&

          \phantom{\{ (\getnext{\prog}(\lab), \varx) \mid}
          \getinst{\prog}(\lab) = \varx \kweq \expr^\lab (\expr^\lab_1 \cdots
          \expr^\lab_n)
        \}\\

        \afsenv' &=& \lambda \lab \in \labset. \; \left\{
          \begin{array}{ll}
            [\varx \mapsto \aval]
            & \text{if} \; (\lab, \varx) \in R\\

            \epsilon
            & \text{otherwise}\\
          \end{array}
        \right.\\
      \end{array}
    \]
\end{itemize}

\paragraph{Programs} Finally, we define the abstract semantics $\asem{\prog}:
\atreeset \rightarrow \aelemset$ of a program $\prog$ with a given syntactic
view:
\[
  \asem{\prog}(\atree) = \lim_{n \rightarrow \infty}(\atransfer)^n \circ
  \entryaelem(\atree)
\]
It is the least fixed point of the abstract transfer function $\atransfer$ with
an abstract entry state $\entryaelem$ depending on the given syntactic view
$\atree$:
\begin{itemize}
  \item \underline{Abstract Transfer Function}: $\atransfer: \aelemset
    \rightarrow \aelemset$
    \[
      \atransfer(\aelem) = \aelem \join \sem{\adcall} \wedge
      \bigjoin_{\lab \in \labset}{\asem{\getinst{\prog}(\lab)}(\lab, \aelem)}
    \]
    where $\aelem = (\adcall, \ascall, \afsenv)$ and $\sem{\adcall} = (\adcall,
    \ascall, [\lab \mapsto \aenv_\lab \mid \lab \in \adcall \wedge
    \getinst{\prog}(\lab) = \varx = \expr(\cdots) \wedge \aenv_\lab = [\varx
    \mapsto \top]])$.
  \item \underline{Abstract Entry States}: $\entryaelem:
    \atreeset \rightarrow \aelemset$
    \[
      \entryaelem(\atree) = (\varnothing, \varnothing, \afsenv)
    \]
    where \[
      \begin{array}{lcl}
        \atree &=& \ty_k \langle \cdots \rangle\\
